---
title: "Simple document"
author: "Nandini M"
date: "2023-09-12"
output: github_document
  #html_document:
    #toc: true
    #toc_float: true
    #code_folding: hide
---

```{r, echo=FALSE, message=FALSE}
# eval=FALSE -> shows code but doesn't run it
# echo=FALSE -> don't show the code
# message=FALSE -> don't show output of the code
library(tidyverse)
```


I'm an R Markdown document! 

# Section 1: First code chunk

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

I can take the mean of the sample, too!
The mean is `r round(mean(samp),digits=4)`.

# Section 2: Make a plot

This code is borrowed from last lecture; it creates a dataframe for plotting.

```{r}
plot_df = 
  tibble(
    x = rnorm(1000, sd=0.5),
    y = 1+2*x+rnorm(1000)
  )
```

Next up is a histogram of the 'x' variable in 'plot_df'.

```{r}
ggplot(plot_df, aes(x=x)) + geom_histogram()
```

Lastly, I'll make a scatterplot.

```{r}
ggplot(plot_df, aes(x=x,y=y)) + geom_point()
```


# Section 3: Learning assessment

This code chunk should: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created

```{r}
dataf = 
  tibble(
    a = rnorm(500, mean=1),
    b = a > 0,
    c = abs(a)
  )
ggplot(dataf, aes(x=c)) + geom_histogram()
```

# Section 4: Formatting

Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~

Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell
